Using Local PCA to Investigate Population Structure Along the Genome

### 2016-05-05 medicago/local_pca_on_medicago.Rmd
.

Now let's see how it goes to do this for an entire chromosome.
On chromosome 1 there are about 5 million SNPs, so we'll do it in windows of 5,000.
First, windows by SNPs.
```{r lpca_chr1}
sites <- vcf_positions(bcf.file)
win.fn.snp <- vcf_windower(bcf.file, size=5e3, type="snp", sites=sites, samples=get.indivs) 
```

>>>>

Now let's see how it goes to do this for an entire chromosome.
On chromosome 1 there are about 5 million SNPs, so we'll do it in windows of 5,000.
First, windows by SNPs.
```{r lpca_chr1}
sites <- vcf_positions(bcf.file)
win.fn.snp <- vcf_windower(bcf.file, size=5e3, type="snp", sites=sites, samples=get.indivs) 
snp.pca <- eigen_windows(win.fn.snp,k=2)
```
